%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%% CV  Ed Barry 04/2020 %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\PassOptionsToPackage{dvipsnames}{xcolor}
\documentclass[10pt,a4paper]{altacv}

%Layout
\geometry{left=1cm,right=9cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm,footskip=2\baselineskip}

%Packages
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[default]{lato}
\usepackage[hidelinks]{hyperref}
\usepackage{pgfkeys}

%Colors
\definecolor{accent}{HTML}{000e17}
\definecolor{heading}{HTML}{C86733}
\definecolor{emphasis}{HTML}{363636}
%\definecolor{emphasis}{HTML}{696969}
\definecolor{body}{HTML}{01415f}

\colorlet{heading}{heading}
\colorlet{accent}{accent}
\colorlet{emphasis}{emphasis}
\colorlet{body}{body}

\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%   BEGIN THE CV DOCUMENT %%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
\name{Ed \, Barry}
\personalinfo{
    % \printinfo{\faBirthdayCake}{8th Jan 1992}
    \email{ed.barry@netc.fr}
    \phone{0481 320 570}
%    \mailaddress{SR Njemačke 6, 10000}
    \location{Brisbane, AUS}
     \linkedin{https://www.linkedin.com/in/edmbarry/}
    \github{https://github.com/edmbarry}
    \scholar{https://orcid.org/0000-0003-1566-3950}
}

\tagline{\normalsize Adaptable chemical and computational engineer with expertise in process modelling, 
data science and engineering, scientific computing, high performance computing,
laboratory skills, and machine learning.}

\begin{fullwidth}
\makecvheader

\end{fullwidth}


\cvsection[page1sidebar]{Experience}

%%%%%%%%%%%%%
%Experience 1
%%%%%%%%%%%%%

\cvevent{Computational Modeller}{Advanced Water Management Centre}{Apr 2015 -- present}{Brisbane, AUS \& London, CAN}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]  \small{\textit{Rationale}: To replace expensive physical 
    prototyping with computational models when scaling up bioreactors.}
    \item[--]   \small{Developed open source partial differential equation
    models to simulate fluids and biochemistry.} 
    \item[--] \small{Deployed models using Linux containers 
    on high performance computing infrastructure.}
    \item[--]  \small{Post-processed data-rich simulation results for 8 papers, 
    technical reports and 3 conferences.}
    \item[--]   \small{Developed scientific libraries in C++ for coupling 
    radiation and biology to model photosynthesis at 
    \href{https://www.trojantechnologies.com/}{Trojan~Technologies} 
    in London, Canada.}
\end{itemize}
\divider\smallskip

%%%%%%%%%%%%%
%Experience 2
%%%%%%%%%%%%%
\cvevent{Software Instructor}{The Carpentries Organization}{Apr 2018 -- present}{Worldwide}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Designed and taught computational thinking, 
    data analysis and software techniques to industry professionals using
    Python for data science, shell for automation, and git for version
    control.}
    \item[--]   \small{Improved my data and statistical workflow 
    efficiencies and those of course attendees based on their feedback.}
\end{itemize}
\divider\smallskip

%%%%%%%%%%%%%
%Experience 3
%%%%%%%%%%%%%
\cvevent{Research Scientist}{Advanced Water Management Centre}{Nov 2019 -- Mar 2020}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Designed and ran experiments on a novel glass 
    recycling process.}
    \item[--]   \small{Discovered analysis technique based on 
    coffee science. Improved waiting times for results from days to minutes.}
    \item[--]   \small{Analysed experimental results with ANOVA, Markov chain Monte
    Carlo, linear and nonlinear regression. Estimated kinetic and operating parameters.}
\end{itemize}
\divider\smallskip

%%%%%%%%%%%%%
%Experience 4
%%%%%%%%%%%%%
\cvevent{Scientific Officer}{Queensland Department of Environment and Science}{Apr 2019 -- Sep 2020}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Prepared a report into the state of leading 
    wastewater treatment practice in the Great Barrier Reef catchment.}
    \item[--]   \small{Conducted interviews, and analysed monitoring 
    and survey data to gain qualitative and quantitative insights.}
    \item[--]   \small{Recommended operation practices across a 
    range of treatment plant sizes with a view to minimise
    nutrient discharge into the Great Barrier Reef.}
\end{itemize}
\divider\smallskip


%%%%%%%%%%%%%
%Experience 5
%%%%%%%%%%%%%
\cvevent{Laboratory Research Assistant}{Advanced Water Management Centre}{Nov 2013 -- Apr 2015}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Operated laboratory- and pilot-scale bioreactors.}
    \item[--]   \small{Designed batch experiments and carried out chemical
    analysis.}
\end{itemize}

\divider\medskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Projects %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newpage
%%%%%%%%%%%%%
% CERTIFICATES
%%%%%%%%%%%%%
\cvsection[page2sidebar]{Certificates}
\cvevent{Epidemics - the Dynamics of Infectious Diseases}{Penn State University}{Mar 2020}{Online (Coursera)}
\cvevent{Julia Scientific Programming}{University of Cape Town}{Mar 2020}{Online (Coursera)}
\cvevent{Machine Learning with Python}{IBM}{Mar 2020}{Online (Coursera)}

%%%%%%%%%%%%%
% CERTIFICATES
%%%%%%%%%%%%%
\cvsection{Teaching and Supervision}
\cvevent{Research Supervisor}{Advanced Water Management Centre}{Nov 2019 -- Mar 2020}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Supervised Master's student for their summer research project.}
    \item[--]   \small{Worked with student on experimental design, laboratory techniques and safety, chemical analysis and statistical analysis.}
\end{itemize}
\divider\smallskip

\cvevent{Lecturer - Wastewater Modelling and Control}{UQ Chemical Engineering}{Jun 2019 -- Nov 2019}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Coordinated course on principles of biological wastewater treatment, 
    common industry models, numerical methods, 
    uncertainty analysis and propagation, 
    continuous and discrete control strategies, 
    and scientific computing.}
\end{itemize}
\divider\smallskip

\cvevent{Guest Speaker}{UQ Chemical Engineering}{Jun 2019 -- Nov 2019}{Brisbane, AUS}
\begin{itemize}
    \setlength{\itemindent}{0.3em}
    \item[--]   \small{Delivered lecture and workshop on analytical 
    and numerical propagation of uncertainty in models.}
    \item[--]   \small{Ran workshop on modelling and data science 
    workflows using RStudio, Jupyter notebooks, and git.}
\end{itemize}


%%%%%%%%%%%%%
%Project 2
%%%%%%%%%%%%%
\cvsection{Awards}

\cveventnodate{Sporting}{}{}{}

\begin{tabular}{rl}
% \small{
2019 & Australian Champion, Underwater Rugby \\
2003-2007 & Australian Medallist, Swimming\\
% }
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Certificates %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Interests %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

 \cvsection{Interests}

 \wheelchart{1.5cm}{0.5cm}{%
   25/10em/accent!30/Cycling and Swimming,
   25/9em/accent!60/Science,
   10/13em/accent!10/Literature,
   20/9em/accent!90/Technology,
   20/8em/accent!20/Coffee
 }


%%New Page
% \clearpage




\end{document}
