%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Education %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\vspace{0.2mm}
\cvsection{Education}
\cvevent{PhD \ in Chemical Engineering}{University of Queensland\\ Trojan Technologies}{Apr 2015 -- Nov 2019}{}
Title: \textbf{\textit{Distributed parameter modelling of phototrophic bioreactor systems.}}
\begin{itemize}
<<<<<<< HEAD
    \item Modelled the growth of bacteria used in biotechnology taking
    into account biochemical processes, fluid flows, and electromagnetic
    radiation in bioreactors.
    \item Used the finite volume method to solve the partial differential equations.
    \item Improved estimate accuracy by including spatial variations compared with
    lumped-parameter modelling.
=======
    \item Developed modelling framework to couple biochemical processes, fluid flows and electromagnetic radiation.
    \item \textcolor{red}{Modelled the growth of bacteria used in biotechnology [emphasise why it is important] by taking into account biochemical processes, fluid flows and electromagnetic radiations in bioreactors }
    \item Demonstrated overestimated bioreactor performance in 0- and 1-D modelling approximations. 
    \item \textcolor{red}{Details about the model on the pde and also on the analysis (statistics)}
    \item \textcolor{red}{Demonstrated that 0- and 1-D modelling approx lead to overestimation of bioreactors performances}
    \item \textcolor{red}{Corrected performance estimates/approximations using 2- and 3-D modelling taking into account spatial effects}
    \item Showed that 2- and 3-D modelling provided better approximations of performance.
>>>>>>> overleaf-2020-04-01-1002
    \item Published in \textit{Water Research} and project was presented in Canada, Cuba and Switzerland. 
\end{itemize}
\divider\smallskip


\cvevent{BE \ in Chemical Engineering (Hons)}{University of Queensland}{Mar 2009 -- Nov 2014}{}
\begin{itemize}
\item Studied a diverse range of general engineering courses during an exchange programme at \'Ecole Centrale Paris.
\end{itemize}
%\textbullet{} \small{First, 75\% Average}
% \begin{tabular}{rll}
% Thesis  & An Introduction to \\
% & Quantum Random Walks\\
% Dissertation & An Investigation into \\
% & Electron-Proton Entanglement\\
% & in the Hydrogen Atom
% \end{tabular}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Skills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Computing Skills}

\cvskill{Python, Julia, Matlab}{5}
\cvskill{MS Office}{5}
\cvskill{Linux, Unix, Containers}{4}
\cvskill{Latex, Markdown}{4}
\cvskill{Git, SQL}{4}
\cvskill{PyTorch, Tensorflow, Spark}{3}
\cvskill{C, C++, Rust}{3}
\cvskill{R, Fortran}{2}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Strengths %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\cvsection{Technical SKills}
% CFD Job
%\cvtag{Differential Equations} \cvtag{Computational Fluid Dynamics} \cvtag{Process Simulation} \cvtag{Deep Learning} \cvtag{Multiphase Modelling} \cvtag{Turbulence Models} \cvtag{Time Series} \cvtag{Probabilistic Programming} \cvtag{Markov Chain Monte Carlo}

% Machine learning job
\cvtag{Differential Equations} \cvtag{Computational Modelling} \cvtag{Simulation} \cvtag{Deep Learning} \cvtag{Regression} \cvtag{Classification} \cvtag{Bayesian Inference} \cvtag{Time Series} \cvtag{Probabilistic Programming} \cvtag{Markov Chain Monte Carlo} \cvtag{Data Wrangling}

% \divider
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Softskills %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \cvsection{Softskills}

% % \cvtag{Learning Potential}
% \cvtag{Team Work}
% % \cvtag{Organisation}
% \cvtag{Agile}
% \cvtag{Observant}
% \cvtag{Responsible}
% \cvtag{Hard-Working}
% % \cvtag{Professionalism}
% % \cvtag{Responsibility}
% % \cvtag{MultiTasking}
% % \cvtag{Work Under Pressure}
% % \cvtag{Agile}
% % \cvtag{Scrum}

% \divider\softskip
% \begin{itemize}
% \item \textcolor{emphasis}{Development Tools -- DB}
% \end{itemize}
% \cvtag{SQL}\cvtag{Oracle}\cvtag{MySQL}\cvtag{PostgreSQL}
% \divider\smallskip

% \begin{itemize}
% \item \textcolor{emphasis}{Development Tools -- IDE}
% \end{itemize}
% \cvtag{Visual Studio}\cvtag{VS Code}\cvtag{IntelliJ}\cvtag{XCode}
% \divider
\smallskip





